$P$ versus $NP$

### 2019-11-17 doc/manuscript.tex
Improved the result

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

>>>>

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

### 2019-11-17 doc/presentation.tex
Improved the result

\begin{theorem}
\label{result}
In our work was proved that we can define a $\textit{NP--complete}$ problem as

@@

\begin{frame}{The classes $2L$ and $2NL$}

\begin{definition}
The class 2L contains those languages that are deterministic logarithmic space reduced to a language in 1L. The class 2NL consists in those languages that are nondeterministic logarithmic space reduced to a language in 1NL.
\end{definition}

@@

\begin{frame}{Inclusion}

We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively. Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.

@@

\begin{frame}{Proof of $L = 2L$: First part}

On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
\end{frame}

\begin{frame}{Proof of $L = 2L$: Second part}

In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

\begin{frame}{Proof of $NL = 2NL$: First part}

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.

\begin{frame}{Proof of $NL = 2NL$: Second part}

In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

@@

In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ since Hartmanis and Mahaney have shown that $1L \neq 1NL$ by looking at a uniform variant of the string non-equality problem from communication complexity theory. Therefore, we prove the complexity class $L$ is not equal to $NL$. Since we show that $L \neq NL$, then we prove the complexity class $P$ is equal to $NP$.

>>>>

\begin{theorem}
\label{result}
In our work was proved that we can define an $\textit{NP--complete}$ problem as

@@

\begin{frame}{The complexity class $LNL$}

\begin{definition}
\label{definition}
The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every element $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
\end{definition}

@@

\begin{frame}{The class $BNL$}

Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).

@@

\begin{frame}{Proof of $LNL = NL$}

We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
\end{frame}

\begin{frame}{Proof of $L \neq NL$}

However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$. Consequently, we prove the complexity class $L$ is not equal to $NL$.

@@

Since we show that $L \neq NL$, then we prove the complexity class $P$ is equal to $NP$.
